Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-16 content/example.tex
implementation paragraph in section 4; stats table in section 2; removed section 5

>>>>

\subsection{Occurrences of Correlated Calls}
How often do correlated calls occur in practice? To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occurred programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat}.

In the table, the number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. 
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The last three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.

\begin{table}
\caption{Frequencies of correlated-call occurrences in the Dacapo benchmarks}\label{tab:dacapostat}
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrr
>{\columncolor[HTML]{FFFFFF}}r 
>{\columncolor[HTML]{FFFFFF}}l r@{}}
\toprule
\textbf{Benchmark}  &
  \multicolumn{1}{c}{\textbf{$|C|$}} & 
  \multicolumn{1}{c}{\textbf{$|C_P|$}} & 
  \multicolumn{1}{c}{\textbf{$|C^\Subset|$}} & 
  \multicolumn{1}{c}{\textbf{$|\rcc|$}} & 
  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C_P|}{|C|}$\end{tabular}}} & 
  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|C_P|}$\end{tabular}}} & 
  \textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|\rcc|}$\end{tabular}} \\ \midrule
\textbf{antlr}      & 7,610                             & 428                                   & 299                              & 70                                   & {\textbf{6\%}}                                                      & {\textbf{70\%}}                                                     & 4                                                                \\
\textbf{bloat}      & 18,157                            & 933                                   & 429                              & 119                                  & {\textbf{5\%}}                                                      & {\textbf{46\%}}                                                     & 4                                                                \\
\textbf{chart}      & 18,101                            & 466                                   & 195                              & 61                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
\textbf{eclipse}    & 3,222                             & 100                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{35\%}}                                                     & 4                                                                \\
\textbf{fop}        & 4,831                             & 129                                   & 40                               & 12                                   & {\textbf{3\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
\textbf{hsqldb}     & 3,573                             & 81                                    & 35                               & 10                                   & {\textbf{2\%}}                                                      & {\textbf{43\%}}                                                     & 4                                                                \\
\textbf{jython}     & 12,149                            & 487                                   & 129                              & 54                                   & {\textbf{4\%}}                                                      & {\textbf{26\%}}                                                     & 2                                                                \\
\textbf{luindex}    & 7,190                             & 188                                   & 79                               & 29                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
\textbf{lusearch}   & 9,043                             & 350                                   & 126                              & 47                                   & {\textbf{4\%}}                                                      & {\textbf{36\%}}                                                     & 3                                                                \\
\textbf{pmd}        & 10,972                            & 219                                   & 68                               & 23                                   & {\textbf{2\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
\textbf{xalan}      & 3,889                             & 110                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{32\%}}                                                     & 4                                                                \\
\textbf{Geom. mean} & \textbf{7,572}                    & \textbf{240}                          & \textbf{91}                      & \textbf{29}                          & {\textbf{3\%}}                                                      & {\textbf{38\%}}                                                     & \textbf{3}                                                       \\ \bottomrule
\end{tabular}
%}
\end{table}

We can see that on average, 3\% of all call sites $C$ are polymorphic call sites $C_P$.
\mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
Out of those call sites, 38\% are correlated call sites $C^\Subset$. We also see that for one correlated-call receiver, there are on average three correlated calls.

### 2014-12-16 content/impl.tex
implementation paragraph in section 4; stats table in section 2; removed section 5

>>>>

\subsection{Implementation of the Correlated-Calls Analysis}
The correlated-calls analysis was implemented in the Scala programming language~\cite{odersky2004overview}. 
We chose Java as the target language for client programs of the analysis.
To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.

Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch. Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.

We tested the implementation of the correlated-calls analysis using an IFDS taint-analysis implementation as a client analysis. We converted the IFDS taint analysis into an IDE problem with an implementation of $\transCC_\rcc$.

We extensively tested the correlated-calls analysis to ensure that in the absence of correlated calls in an input program, the analysis produced the same results as an IFDS-equivalent analysis, and in the presence of correlated calls, the result was more precise.

### 2014-12-16 content/intro.tex
implementation paragraph in section 4; stats table in section 2; removed section 5

This paper presents an approach to dataflow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object. In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviors will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing dataflow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls.

>>>>

This paper presents an approach to dataflow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object.
\mtodo{Should we define the term ``receiver''?}
In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviors will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing dataflow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls.
